%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,21pt]{article}

\usepackage[ukrainian]{babel}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\hypersetup{colorlinks=true,urlcolor=black}

\usepackage{geometry}


\iffalse
% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-1in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1in}
\fi
\geometry{a4paper, left=1cm, right=1cm, top=0.5cm, bottom=1cm, includehead, includefoot}

\setlength{\footskip}{12pt}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyhf{} % clear all header and footer fields
\fancyfoot[C]{\thepage}


\urlstyle{rm}


\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\nonBulletItem}[2]{
  \item[]\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\normalsize{ \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      #3 & #4 \\
    \end{tabular*}}
    \vspace{-5pt}
}

\newcommand{\resumeSubheadingLess}[3]{
  \vspace{-1pt}\item\normalsize
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}
    \vspace{0pt}
    \small{\newline #3}
    \vspace{-4pt}
}

\newcommand{\nonBulletResumeSubheading}[4]{
  \vspace{-1pt}\normalsize{ \item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      #3 & #4 \\
    \end{tabular*}}
    \vspace{-5pt}
}

\newcommand{\subItemOfItem}[1]{
    \item\small {#1}\vspace{-2pt}
}

\newcommand{\resumeSectionType}[2]{
  \item\begin{tabular*}{0.96\textwidth}[t]{
    p{0.3\linewidth}p{0.7\linewidth}
  }
    \textbf{#1} & #2
  \end{tabular*}\vspace{-6pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}
\newcommand{\nonBulletResumeSubItem}[2]{\nonBulletItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}
\renewcommand\thefootnote{\textcolor{black}{\textbf{\arabic{footnote}}}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center} \textbf{\LARGE{Yehor Kozyr}} \end{center}
\vspace{-12pt}
\begin{center}
\href{https://www.linkedin.com/in/yehor-kozyr/}{linkedin.com/in/yehor-kozyr} $\vert$ +31687852493 $\vert$ \href{mailto:yehor.kozyr@gmail.com}{yehor.kozyr@gmail.com} $\vert$ \href{https://github.com/Sne4kers}{github.com/Sne4kers} \end{center}

%\vspace{-15pt}  

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \nonBulletResumeSubheading
      {Delft University of Technology}{Delft, Netherlands}
      {\textbf{Bachelor of Computer Science and Engineering with Honours;  GPA: 8.9/10}}{August 2021 - June 2024}
      \vspace{6pt}
      \scriptsize {\small{Related coursework: Computational Intelligence, Machine Learning, Big Data Processing, Data Mining, Software Quality and Testing}}\\
      \vspace{-3pt}
      \resumeItemListStart
      \subItemOfItem{\small{Teaching assistant for the Data Mining course: implemented solutions for the exercises, set up grading environment for code submissions, grading student's text submissions}}
      \resumeItemListEnd
      %\vspace{4pt}
      \scriptsize {\small{Minor: \textbf{Quantum Science and Quantum Information}}}\\
      %\vspace{-4pt}
      \scriptsize {\small{Related coursework: Quantum Physics, Quantum Communication and Computation, Solid-State Quantum Bits}}
  \nonBulletResumeSubheading  
      {Kyiv Natural-Scientific Lyceum No. 145}{Kyiv, Ukraine}
      {High school student; GPA: 11.2/12}{September 2017 - June 2021}
      \resumeItemListStart
          \subItemOfItem{Curriculum focused on Mathematics, Physics, Computer Science}
          \subItemOfItem{Participated in Olympiads winning regional level and reaching qualifications stage for the national level in Mathematics}
          \subItemOfItem{Published a paper on the 1-dimensional random walk as a part of Junior Academy of Sciences of Ukraine Competition }
      \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-10pt}
\section{Research Projects}
\resumeSubHeadingListStart
    \nonBulletResumeSubheading{Research on AI-assisted testing}{Delft, Netherlands}{CISELab}{September 2023 - December 2023}
    \vspace{6pt}
    \small{\newline{} The project is part of my work as a research assistant at CISELab related to the application of multi-objective search-based algorithms for software and cyber-physical systems testing.}
    \vspace{-4pt}
        \resumeItemListStart
            \subItemOfItem
            {Studied papers on \textbf{multi-objective reinforcement learning} and \textbf{search algorithms} for software engineering applications.}
            \subItemOfItem
            {Implemented and experimented with Deep Q-Networks, \textbf{evolutionary algorithms} for search-based test case generation software.}
            \subItemOfItem
            {Pivoted the project to participate in the Search-Based and Fuzz Testing ICSE’24 workshop's\footnote{ICSE’24 workshop on Search-Based and Fuzz Testing 2024 - \href{https://sbft24.github.io/}{sbft24.github.io}} tool competition on UAV testing.}
            \subItemOfItem
            {Analysed and benchmarked different reinforcement learning approaches for testing of the \textbf{PX4-Avoidance algorithm}.}
            \subItemOfItem
            {Experimented with different sets of objectives, based on different similarity functions, crash locations, sizes of obstacles, and population selection techniques.}          
        \resumeItemListEnd
    \nonBulletResumeSubheading{Research on simple temporal networks}{Delft, Netherlands}{STAR Lab}{September 2022 - Present}
    \vspace{6pt}
    \small{\newline{} The project is part of the Honours program at TU Delft and is focused on benchmarking and improving decremental algorithms in simple temporal networks that take advantage of the idea of a support graph.}
    \vspace{-4pt}
        \resumeItemListStart
            \subItemOfItem
            {Studied papers on the proposed and already existing algorithms for finding minimal weights in simple temporal networks.}
            \subItemOfItem
            {Developed a benchmarking setup to compare the proposed algorithm with an existing solution on randomly generated graphs.}
            \subItemOfItem
            {Identified weaknesses in the algorithm using a \textbf{profiler}, running it on graphs of sizes from 100 to 3000 vertices.}
            \subItemOfItem
            {Improved the graph library used for the project by increasing test coverage and reducing the cyclomatic complexity of vertex removal methods.}
            \subItemOfItem
            {Improved the proposed algorithm by reducing the complexity of some functions from $O(n^3)$ to $O(mn)$ and from $O(n\cdot log(n) + m)$ to $O(m\cdot log(n) + m)$, resulting in \textbf{better performance than the existing solution}.}
            \subItemOfItem
            {Currently conducting experiments with different graph and update generators and writing a paper on found results.}
        \resumeItemListEnd
\resumeSubHeadingListEnd



%-----------PROJECTS-----------------
\vspace{-8pt}
\section{Work Experience}
  \resumeSubHeadingListStart
      \nonBulletResumeSubheading{Software Developer Intern - Presenter tracking}{Delfgauw, Netherlands}
    {Avonic}{April 2023 - June 2023}
    \vspace{6pt}
    \scriptsize { \small{\newline{} Middleware software that integrates a camera with a microphone array, allowing for tracking speakers based on audio information.}}
    \vspace{-4pt}
    \resumeItemListStart
        \subItemOfItem
            {Worked in a team of 5 interns on the Python project. Organized the workflow with the \textbf{Scrum} framework.}
         \subItemOfItem
            {Developed a \textbf{Flask} application with 46 endpoints, that controlled \textbf{multiple threads} for tracking and information updates.}
        \subItemOfItem
            {Expanded a mathematical model for tracking using vector geometry reducing the calculation time by \textbf{10\%}.}
        \subItemOfItem
            {Improved total \textbf{test coverage} from \textbf{75\% to 93\%}, introducing tests for the Flask application.}
        \subItemOfItem
            {Deployed the system onto NVidia Jetson Nano with custom compiled \textbf{FFMPEG} to reduce processing time for \textbf{YOLO} system.}
        \subItemOfItem
            {Introduced \textbf{mutation testing} to the project, and enhanced mutation coverage from \textbf{40\% to 82\%}.}
        \subItemOfItem
            {Modernized \textbf{GitLab CI pipeline} by adding test coverage reports which led to an increase of the \textbf{pylint} score from 5.6 to 9.2.}
      \resumeItemListEnd
    \nonBulletResumeSubheading{Software Developer - SynTest Framework}{Delft, Netherlands}
    {CISELab, TU Delft}{December 2022 - September 2023}
    \vspace{6pt}
    \scriptsize { \small{\newline{}Open-source framework written in TypeScript for generating synthetic tests with fuzzing for programs in Javascript-based languages.}}
    \vspace{-4pt}
    \resumeItemListStart
        \subItemOfItem
          {Optimized the \textbf{fitness function} reducing the time complexity of the precalculation stage from cubic to quadratic.}
        \subItemOfItem
          {Created a plugin for publishing events to \textbf{RabbitMQ} and WebSockets for tracking generation's progress.}
        \subItemOfItem
          {Researched alternatives of \textbf{multi-objective reinforcement learning} algorithms for \textbf{fuzzing}.}
      \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-6pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubheadingLess{Ray-tracing application}{September 2022 - October 2022}{Part of the Computer Graphics course with the goal of implementing a rendering engine for custom scenes created in Blender.}
    \resumeItemListStart
        \subItemOfItem{Collaborated with 2 students to implement a project in \textbf{C++} with OpenGL, tested using \textbf{GTest}.}
        \subItemOfItem
        {Implemented Phong reflection model, \textbf{ray-tracing} with reflections, lights, and area lights, supporting hard and soft shadows.}
        \subItemOfItem
        {Modified camera view to support multiple rays per pixel with irregular sampling and \textbf{depth of field effect}.}
        \subItemOfItem
        {Introduced visual debug functionality and used it for manual debugging.}
    \resumeItemListEnd
\resumeSubheadingLess{Back-end for pizza ordering application}{November 2022 - January 2023}{The project consists of multiple microservices managing a full cycle of ordering pizza, facilitating users’ and store owners’ needs.}
    \resumeItemListStart
        \subItemOfItem
        {Navigated a team of 6 people in developing a project with the use of \textbf{Java Spring} and Gradle, tested with JUnit and PIT.}
        \subItemOfItem
        {Designed project architecture of 5 microservices and systematized project requirements with the \textbf{MoSCoW method}.}
        \subItemOfItem
        {Implemented an interface for a shopping cart database with 5 entities and used it to satisfy users’ requests via \textbf{REST API}.}
        \subItemOfItem
        {Modified authentication to accommodate users with different access and added support on all projects' microservices.}
        \subItemOfItem
        {Identified \textbf{code smells} and refactored code, reducing the project's maximum weighted methods per class from 60 to 30.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Publications}
\begin{description}[font=$\bullet$]
\item {Y. Kozyr, “Одновимiрне випадкове симетричне блукання точки,” [One-dimensional symmetric random walk] in Proc. Shevchenkivska Vesna – 2020. (ShV’20), Apr. 25-26, 2020. [Online]. - p. 18-19 Available:~\href{https://probability.knu.ua/shv2020/ShV_2020.pdf}{https://probability.knu.ua/shv2020/ShV\_2020.pdf}}
\end{description}

\vspace{-5pt}
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {Participant at the National Junior Academy of Sciences Competition (Math) - 2020}
\vspace{-5pt}
\item {1st place at the Kyiv Junior Academy of Sciences Competition (Math) - 2020}
\vspace{-5pt}
\item {2nd place at the Kyiv Olympiad in Informatics - 2019}
\vspace{-5pt}
\item {2nd place at the Kyiv Olympiad in Mathematics, participant of Qualifications for National stage - 2019}
\vspace{-5pt}
\item {3rd place at the Second Stage of 2019 All-Ukrainian Collegiate Programming Contest - 2019}
\vspace{-5pt}
\item {3rd place at the Computer Experiment Team Olympiad - 2019}
\vspace{-5pt}
\item {1st place at the Kyiv Olympiad in Physics, participant of Qualifications for National stage - 2019}
\end{description}


\vspace{-5pt}
\section{Skills Summary}
    \resumeSubHeadingListStart
        \resumeSectionType{Programming Languages}{C++, Java, Python, Scala, TypeScript, SQL}
        \resumeSectionType{Tools}{GIT, PostgreSQL, Jupyter Notebooks, \LaTeX}
        \resumeSectionType{Platforms}{Linux, Web, Windows, Arduino, AWS, Raspberry PI}
        \resumeSectionType{Soft Skills}{Collaboration, Leadership, Event Management, Public Speaking}
        \resumeSectionType{Languages}{English - Fluent, Ukrainian - Native}
    \resumeSubHeadingListEnd

\vspace{-6pt}
\section{Extracurricular Activities}
  \resumeSubHeadingListStart
	\nonBulletResumeSubheading
    {Mathematics Teacher at Kvanta Math courses}{Kyiv, Ukraine}
    {Explained topics, helped students during classes, and graded their homework.}{September 2019 - June 2021}
    % \vspace{10pt}\textbf{\large{Community Experience}}
    \nonBulletResumeSubheading
    {Member of the School Student Council}{Kyiv, Ukraine}
    {Participated at every stage of organizing extracurricular activities for students.}{September 2018 - May 2021}

\resumeSubHeadingListEnd

\end{document}